---
title: "Publications"
favicon: images/headphones.JPG
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    css:
      - css/custom.css
---

<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons/css/academicons.min.css">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
library(distilltools)
```

```{r metathis, message=FALSE, warning=FALSE, include=FALSE}
library(metathis)
meta() %>%
  meta_description(
    "Open-Source Software"
  ) %>%
  meta_name("github-repo" = "donaldRwilliams/donaldRwilliams.github.io") %>%
  meta_viewport() %>%
  meta_social(
    title = "DRW: Software",
    url = "https://donaldrwilliams.github.io/publications.html",
    image = "https://donaldrwilliams.github.io/images/pub_preview.png",
    image_alt = "A photo of DRW",
    og_type = "website",
    og_author = c("Donald R. Williams"),
    twitter_card_type = "summary",
    twitter_creator = "@wdonald_1985"
  )
```

```{r, include=FALSE}
library(htmltools)
source("R/functions.R")
```



<center>
```{r, echo=FALSE}
icon_link(
    icon = "ai ai-google-scholar",
    text = "Google Scholar",
    url  = "https://scholar.google.com/citations?user=IjPXPAMAAAAJ&hl=en"
)
```
</center>



## Peer-Reviewed

**Williams, D. R.** (in press). Learning to Live with Sampling Variability: 
Expected Replicability in Partial Correlation Networks. *Psychological Methods*.

```
@article{,
  title={Learning to live with sampling variability: Expected 
         replicability in partial correlation networks},
  author={Williams, Donald R},
  year={2020},
  journal={PsyArXiv},
  doi={10.31234/osf.io/fb4sa}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/fb4sa/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/uedkj/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)
```

<br>

**Williams, D. R.** (2021) Bayesian Estimation for Gaussian Graphical Models: 
Structure Learning, Predictability, and Network Comparisons, Multivariate Behavioral Research, 56:2, 336-352,  `r doi("10.1080/00273171.2021.1894412")` 

```
@article{,
  title={Bayesian estimation for Gaussian graphical models: 
         Structure learning, predictability, and network 
         comparisons},
  author={Williams, Donald R},
  journal={Multivariate Behavioral Research},
  volume={56},
  number={2},
  pages={336--352},
  year={2021},
  publisher={Taylor \& Francis},
  doi = {10.1080/00273171.2021.1894412}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/x8dpr/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/k9mv2/"
  )

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)
```

<br>

**Williams, D. R.**, Martin, S. R., & Rast, P. (in press). Putting the Individual into Reliability: Bayesian Testing of Homogeneous Within-Person Variance in Hierarchical Models. *Behavior Research Methods*.


```
@article{,
  title={Putting the individual into reliability: 
         Bayesian testing of homogeneous within-person 
         variance in hierarchical models},
  author={Williams, Donald R and Martin, Stephen R and 
          Rast, Philippe},
  year={2019},
  publisher={PsyArXiv},
  doi={10.31234/osf.io/hpq7w}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/hpq7w/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/2qesh/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMncv/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/vICC"
)
```


<br>

**Williams, D. R.**, Liu, S., Martin, S. R., & Rast, P. (2021). Bayesian 
Multivariate Mixed-Effects Location Scale Modeling of Longitudinal Relations among 
Affective 
Traits, States, and Physical Activity.
European Journal of Psychological Assessment. 36 (6). `r doi("10.1027/1015-5759/a000624")`

```
@article{,
  title={Bayesian Multivariate Mixed-Effects Location 
         Scale Modeling of Longitudinal Relations among 
         Affective Traits, States, and Physical Activity},
  author={Williams, Donald R and Martin, Stephen R and Liu, Siwei and Rast, Philippe},
  journal={European Journal of Psychological Assessment},
  year={2021},
  publisher={Hogrefe Publishing},
  doi={10.1027/1015-5759/a000624}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/4kfjp/"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/3bmdh/"
)
```



## Pre-Prints

