---
title: "Publications"
favicon: images/headphones.JPG
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    css:
      - css/custom.css
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
library(distilltools)
```

```{r metathis, message=FALSE, warning=FALSE, include=FALSE}
library(metathis)
meta() %>%
  meta_description(
    "Publications"
  ) %>%
  meta_name("github-repo" = "donaldRwilliams/donaldRwilliams.github.io") %>%
  meta_viewport() %>%
  meta_social(
    title = "DRW: Publications",
    url = "https://donaldrwilliams.github.io/publications.html",
    image = "https://donaldrwilliams.github.io/images/pub_preview.png",
    image_alt = "A photo of DRW",
    og_type = "website",
    og_author = c("Donald R. Williams"),
    twitter_card_type = "summary",
    twitter_creator = "@wdonald_1985"
  )
```

```{r, include=FALSE}
library(htmltools)
source("R/functions.R")
```



<link rel="stylesheet" 

href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons/css/academicons.min.css">


## Peer-Reviewed

First author: 16 

* Highlights  (all first author)
  + Behavior Research Methods: 2
  + Journal of Mathematical Psychology: 1
  + Journal of Open-Source Software: 1 (single author)
  + **Psychological Methods**: 3 (including 1 single author)
  + British Journal of Mathematical and Statistical Psychology: 1
  + Multivariate Behavioral Research: 2 (including 1 single author)
 

<font size="2"> (note: 9 first author manuscripts are in review. 
see pre-prints.)</font> 


### 2021
**Williams, D. R.** (in press). Learning to Live with Sampling Variability: 
Expected Replicability in Partial Correlation Networks. *Psychological Methods*.

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/fb4sa/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/uedkj/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)


icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/net_enr"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.** (2021) Bayesian Estimation for Gaussian Graphical Models: 
Structure Learning, Predictability, and Network Comparisons, Multivariate Behavioral Research, 56:2, 336-352,  `r doi("10.1080/00273171.2021.1894412")` 


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/x8dpr/download"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/net_mbr_solo"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, Martin, S. R., & Rast, P. (in press). Putting the Individual into Reliability: Bayesian Testing of Homogeneous Within-Person Variance in Hierarchical Models. *Behavior Research Methods*. 


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/hpq7w/download"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMncv/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/vICC"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/net_mbr_solo"
)

```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, Liu, S., Martin, S. R., & Rast, P. (2021). Bayesian 
Multivariate Mixed-Effects Location Scale Modeling of Longitudinal Relations 
among Affective Traits, States, and Physical Activity. European Journal 
of Psychological Assessment. 36 (6). `r doi("10.1027/1015-5759/a000624")`

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/4kfjp/"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/3bmdh/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/mv_melsm"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

Mulder, J., **Williams, D. R.**, Gu, X., Olsson-Collentine, A., Tomarken, A., 
Boing-Messing, F., Hoijtink, H., ... & van Lissa, C. (in press). BFpack: Flexible bayes factor testing of scientific theories
in R. *Journal of Statistical Software*.

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://arxiv.org/pdf/1911.07728"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BFpack/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/jomulder/BFpack"
)


icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/bfpack"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

### 2020

**Williams, D. R.**, Mulder, J., Rouder, J. N., & Rast, P. (2020). 
Beneath the surface: Unearthing within-person variability and mean 
relations with Bayesian mixed models. *Psychological Methods*. 
`r doi("10.1037/met0000270")`

These analyses are reproduced at the GitHub repo.

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/gwatq/download"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/hypMuVar"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/beneath"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.** & Joris Mulder. Bayesian Hypothesis Testing for Gaussian Graphical Models: Conditional Independence and Order Constraints. *Journal of Mathematical Psychology*, 99, 102441. `r doi("10.1016/j.jmp.2020.102441")``

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/ypxd8/download"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
    )

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/net_hyp_jmp"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, Rast, P., Pericchi, L. R., & Mulder, J. (2020). 
Comparing Gaussian graphical models with the posterior predictive 
distribution and Bayesian model selection. *Psychological methods*.
`r doi("10.1037/met0000254")``


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/yt386/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/7hyr4/"
  )

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/ggm_compare"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, & Rast, P. (2020). Back to the basics: Rethinking 
partial correlation network methodology. *British Journal of Mathematical and Statistical Psychology*, 73(2), 187-212.  `r doi("10.1111/bmsp.12173")``





```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/fndru/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/c62pb/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/back_to_basics"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, & Mulder, J. (2020). BGGM: Bayesian Gaussian Graphical 
Models in R. Journal of Open Source Software, 5(51), 2111. `r doi("10.21105/joss.02111")`



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://www.theoj.org/joss-papers/joss.02111/10.21105.joss.02111.pdf"
)


icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/bggm_joss"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, & Burkner, P. (2020). Coding errors lead to unsupported conclusions: a critique of Hofmann et al. (2015). Meta-Psychology, 4.
`r doi("10.15626/MP.2018.872")`.



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://open.lnu.se/index.php/metapsychology/article/view/872/2286"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/kd3en/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/coding_errors"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

Briganti, G., **Williams, D. R.**, Mulder, J., & Linkowski, P. (2020). Bayesian network structure and predictability of autistic traits.
*Psychological Reports*. `r doi("10.1177/0033294120978159")`.

```{r, echo=FALSE}
icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/bggm_autism"
)

```

<hr style="width:35%;text-align:left;margin-left:15">  

Jones, P. J., **Williams, D. R.**, & McNally, R. J. (2020).
Sampling variability is not nonreplication: A Bayesian reanalysis
of Forbes, Wright, Markon, and Krueger.
*Multivariate Behavioral Research*, 1-7.
`r doi("10.1080/00273171.2020.1797460")`




```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/egwfj/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/g5etn/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/forbes_comment"
)

```


<hr style="width:35%;text-align:left;margin-left:15">  

Rast, P., Martin, S. R., Liu, S., & **Williams, D. R.** (2020). A new
frontier for studying within-person variability: Bayesian multivariate
generalized autoregressive conditional heteroskedasticity models.
*Psychological Methods*. `r doi("10.1037/met0000357")``


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/j57pk/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/nef2q/"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/ph-rast/bmgarch"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/pm_garch"
)

```


<hr style="width:35%;text-align:left;margin-left:15">  

### 2019

**Williams, D. R.**, Zimprich, D. R., & Rast, P. (2019). 
A Bayesian nonlinear mixed-effects location
scale model for learning. *Behavior research methods*, 51(5), 
1968-1986. `r doi("10.3758/s13428-019-01255-9")`.


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://link.springer.com/content/pdf/10.3758/s13428-019-01255-9.pdf"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/nlmelsm"
)

```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, Rhemtulla, M., Wysocki, A. C., & Rast, P. (2019). On nonregularized estimation of psychological networks. *Multivariate behavioral research*, 54(5), 719-750. `r doi("10.1080/00273171.2019.1575716")`.



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/xr2vf/download"
)

icon_link(
    icon = "fab fa-github",
    text = "Repo",
    url  = "https://github.com/donaldRwilliams/on_nonregularized_networks"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/on_nonreg"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

Nalborczyk, L., Burkner, P. C., & **Williams, D. R.** (2019). Pragmatism 
should not be a substitute for statistical literacy, a commentary on Albers, 
Kiers, and van Ravenzwaaij (2019). *Collabra: Psychology*,
5(1). `r doi("10.1525/collabra.197")`




```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://online.ucpress.edu/collabra/article-pdf/5/1/13/437386/197-2975-1-pb.pdf"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/nmp6x/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/pragmatism"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

### 2018

Quintana, D. S., & **Williams, D. R.** (2018). Bayesian alternatives for 
common null-hypothesis significance tests in psychiatry: a non-technical 
guide using JASP. BMC psychiatry, 18(1), 178. 
`r doi("10.1186/s12888-018-1761-4")`



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://bmcpsychiatry.biomedcentral.com/track/pdf/10.1186/s12888-018-1761-4.pdf"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/emz4r/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/jasp"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

Lakens, D., Adol, F. G., Albers, C. J., Anvari, F., Apps, M. A., Argamon, S. E., ... & Buchanan, E. M. (2018). Justify your alpha. *Nature Human Behaviour*, 2(3), 168.




```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/9s3y6/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/by2kc/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/justify_alpha"
)
```


<hr style="width:35%;text-align:left;margin-left:15"> 

Carlsson, R., Agerstrom, J., **Williams, D.R**, & Burns, G. N. (2018). A Primer on the benenits of differential treatment analysis when predicting discriminatory behavior. *Quantitative Methods for Psychology*, 14(3), 193-198. 
`r doi("10.20982/tqmp.14.3.p193")`.



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "http://www.tqmp.org/RegularArticles/vol14-3/p193/p193.pdf"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/primer_tqmp"
)
```


<hr style="width:35%;text-align:left;margin-left:15"> 


Merritt, J. R., Davis, M. T., Jalabert, C., Libecap, T. J., **Williams, D. R.**, Soma, K. K., & Maney, D. L. (2018). Rapid effects of estradiol on aggression 
depend on genotype in a species with an estrogen receptor polymorphism. 
Hormones and behavior, 98, 210-218. `r doi("10.1016/j.yhbeh.2017.11.014")``



```{r, echo=FALSE}
icon_link(
    icon = "fas fa-external-link-alt",
    text = "Journal",
    url  = "https://www.sciencedirect.com/science/article/abs/pii/S0018506X17303501"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/rapid_effects"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

### 2017

**Williams, D. R.**, Carlsson, R., & Burkner, P. C. (2017). Between-litter 
variation in developmental studies of hormones and behavior: In
ated false positives and diminished power. Frontiers in
neuroendocrinology, 47, 154-166. `r doi("10.1016/j.yfrne.2017.08.003")`




```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/97xjz/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/fxy7h/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/between_litter"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, & Burkner, P. C. (2017). Effects of intranasal oxytocin 
on symptoms of schizophrenia: a multivariate Bayesian meta-analysis. *Psychoneuroendocrinology*, 75, 141-151. 
`r doi("10.1016/j.psyneuen.2016.10.013")`




```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/qf5zn/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/6pyfu/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/mv_ot"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

Burkner, P. C., **Williams, D. R.**$^*$, Simmons, T. C., & Woolley, J. D. 
(2017). Intranasal oxytocin may improve high-level social cognition 
in Schizophrenia, but not social cognition or neurocognition in
general: a multilevel bayesian meta-analysis. *Schizophrenia Bulletin*, 
43(6), 1291-1303. `r doi("10.1093/schbul/sbx053")``

$^*$ shared 1st authorship




```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/2a4yt/"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/rn6vj/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/cog_ot"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, & Burkner, P. C. (2017). Data extraction and 
statistical errors: A quantitative critique of Gumley, 
Braehler, and Macbeth (2014). *British Journal of Clinical 
Psychology*, 56(2), 208-211. `r doi("10.1111/bjc.12130")`




```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/bw2ce/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/bw2ce/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/gumley_comment"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

Carlsson, R., Schimmack, U., **Williams, D. R.**, & Burkner, P. C. (2017).
Bayes factors from pooled data are no substitute for 
Bayesian meta-Analysis: commentary on Scheibehenne, Jamil, 
and Wagenmakers (2016). *Psychological science*, 28(11), 1694-1697.
`r doi("10.1177/0956797616684682")``



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/axhsr/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/6g9su/components?mode=&view_only="
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/bf_pooled"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  


Maninger, N., Mendoza, S. P., **Williams, D. R.**, Mason, W. A., 
Cherry, S. R., 
Rowland, D. J., ... & Bales, K. L. (2017). Imaging, behavior and 
endocrine analysis of "Jealousy" in a monogamous primate.
*Frontiers in ecology and evolution*, 5, 119.
`r doi("10.3389/fevo.2017.00119")`



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://www.frontiersin.org/articles/10.3389/fevo.2017.00119/pdf"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/jealousy"
)
```



<hr style="width:35%;text-align:left;margin-left:15">  

Bales, K. L., del Razo, R. A., Conklin, Q. A., Hartman, S., 
Mayer, H. S., Rogers, F. D., ... & Witczak, L. R. (2017). 
Focus: Comparative medicine: Titi monkeys as a novel non-human 
primate model for the neurobiology of pair bonding. 
The Yale journal of biology and medicine, 90(3), 373.


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5612182/pdf/yjbm_90_3_373.pdf"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/titi_yale"
)
```




<br>
<br>

## Pre-Prints


First author: 9

* Highlights  (all first author)
  
  + R Journal: 1 (single author)
  + **Psychometrika**: 1 (single author)
  + Multivariate Behavioral Research: 2
  + Behavior Research Methods: 1 (single author)
  + Journal of Open-Source Software: 1 (single author)
  + **Psychological Methods**: 3 (including 1 single author)

<font size="2"> (note: status provided below.)</font> 


### 2021

**Williams, D. R.**, Rodriguez, J. E., & Burkner, P. (2021). 
Putting Variation into Variance: Modeling Between-Study 
Heterogeneity in Meta-Analysis. *PsyArXiv*. 
`r doi("10.31234/osf.io/9vkqy")`

*Psychological Methods*: submitted

The code to reproduce the analyses is on GitHub.



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/9vkqy/download"
)

icon_link(
    icon = "fab fa-github",
    text = "Repo",
    url  = "https://github.com/donaldRwilliams/putting_variance_blsmeta"
)

icon_link(
    icon = "fab fa-github",
    text = "Package",
    url  = "https://github.com/donaldRwilliams/blsmeta"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/putting_variation"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.** (2021). Many Mixture Components, Oh My: Extending 
the Spike and Slab to Bayesian Hypothesis Testing with Multinoulli 
Indicators. *PsyArXiv*. `r doi("10.31234/osf.io/xcvby")`

*Behavior Research Methods*: in review




```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/xcvby/download"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/many_mixtures"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.** (2021). GGMnonreg: Non-Regularized Gaussian 
Graphical Models in R. *PsyArXiv*. `r doi("10.31234/osf.io/p5jk9")`.

*Journal of Open-Source Software*: in review



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/p5jk9/download"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/ggmnonreg_joss"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  


**Williams, D. R.** (2021). The Confidence Interval that Wasn't: 
Bootstrapped Confidence Intervals" in L1-Regularized Partial 
Correlation Networks. *PsyArXiv*. 
`r doi("10.31234/osf.io/kjh2f")``

*Psychological Methods*: submitted

The code to reproduce the simulations is on GitHub.

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/kjh2f/download"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/no_confidence_lasso"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/lasso_ci"
)
```



<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, Briganti, G., Linkowski, P., & Mulder, J. 
(2021). On Accepting the Null Hypothesis of Conditional 
Independence 
in Partial Correlation Networks: A Bayesian Analysis.
*PsyArXiv*. `r doi("10.31234/osf.io/7uhx8")`


*Multivariate Behavioral Research*: in review

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/7uhx8/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/yz5u9/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/net_null"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

Rodriguez, J. E., **Williams, D. R.**, & Rast, P. (2021). Who Is 
and Is Not "Average"?  Random Effects Selection 
with Spike-and-Slab Priors. *PsyArXiv*. `r doi("10.31234/osf.io/4d9tv")`

*Psychological Methods*: in review



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/4d9tv/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/n2z49/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/who_is_average"
)
```



<hr style="width:35%;text-align:left;margin-left:15">  

Rodriguez, J. E., & **Williams, D. R.** (2021). Painless 
Posterior Sampling: Bayesian Bootstrapped Correlation 
Coefficients. *PsyArXiv*. `r doi("10.31234/osf.io/v2chs")`

*The Quantitative Methods for Psychology*: in review

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/v2chs/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/f8syz/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BBcor/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BBcor"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/bbcor"
)
```



<hr style="width:35%;text-align:left;margin-left:15">  

Jongerling, J., Epskamp, S., & **Williams, D. R.** (2021). 
Bayesian Uncertainty Estimation for Gaussian Graphical Models 
and Centrality Indices. *PsyArXiv*. `r doi("10.31234/osf.io/7kude")`


*Multivariate Behavioral Research*: in revision

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/7kude/download"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/JoranJ/BayesGGM"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/bayes_centrality"
)
```



<hr style="width:35%;text-align:left;margin-left:15">  

### 2020

**Williams, D. R.**, & Rodriguez, J. (2020). Why Overfitting is Not 
(Usually) a Problem in Partial Correlation Networks. *PsyArXiv*.
`r doi("10.31234/osf.io/8pr9b")``

*Psychological Methods*: revision


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/8pr9b/download"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/overfitting"
)
```

<hr style="width:35%;text-align:left;margin-left:15"> 


**Williams, D. R.**, Martin, S. R., DeBolt, M., Oakes, L., & Rast, P. (2020). 
A fine-tooth comb for measurement reliability: Predicting true 
score and error variance in hierarchical models. *PsyArXiv*.
`r doi("10.31234/osf.io/2ux7t")``

*Multivariate Behavioral Research*: in review


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/2ux7t/download"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/stephensrmmartin/ICCier"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/finetooth"
)

```


<hr style="width:35%;text-align:left;margin-left:15"> 


**Williams, D. R.** (2020). GGMncv: Nonconvex Penalized Gaussian Graphical Models in R.
*PsyArXiv*. `r doi("10.31234/osf.io/6jz5m")``

*R Journal*: submitted


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/6jz5m/download"
)


icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMncv/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMncv"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/ggmncv"
)

```


<hr style="width:35%;text-align:left;margin-left:15"> 


**Williams, D. R.** (2020). Beyond Lasso: A Survey of Nonconvex 
Regularization in Gaussian Graphical Models. *PsyArXiv*.
`r doi("10.31234/osf.io/ad57p")`

*Psychometrika*: in review


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/ad57p/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/mxku9/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMncv/index.html"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/ggmncv"
)

```


<hr style="width:35%;text-align:left;margin-left:15"> 


Heck, D. W., Boehm, U., Boing-Messing, F., Burkner, P. C., Derks, 
K., Dienes, Z., ... & Hoijtink, H. (2020). A Review of Applications 
of the Bayes Factor in Psychological Research. *PsyArXiv*.

*Psychological Methods*: in review



```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/cu43g/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/k9c5q/"
)



icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/bf_review"
)

```


<hr style="width:35%;text-align:left;margin-left:15"> 

### 2018


**Williams, D. R.**, Rast, P., & Burkner, P. C. (2018). Bayesian
Meta-Analysis with Weakly Informative Prior Distributions. *PsyArXiv*.


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/7tbrm/"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/9n4zp/"
)

icon_link(
    icon = 'fas fa-file-code',
    text = "BibTex",
    url  = "https://github.com/donaldRwilliams/donaldRwilliams.github.io/raw/main/citations_botton/meta_weakly"
)
```


<br>
<br>

## Working Papers


<!-- Williams, D. R. (2020). vICC: Varying Intraclass Correlation Coecients in R. PsyArXiv. -->
<!-- Working paper -->

<!-- Rodriguez, J. E., Williams, D. R., Rast, P., & Mulder, J. (2020). On formalizing theoretical -->
<!-- expectations: Bayesian testing of central structures in psychological networks. PsyArXiv. -->
<!-- Working paper -->

<!-- Martin, S. R., Williams, D. R., & Rast, P. (2019). Measurement invariance assessment with -->
<!-- Bayesian hierarchical inclusion modeling. PsyArXiv. -->
<!-- Working paper -->

<!-- Williams, D. R., Piironen, J., Vehtari, A., & Rast, P. (2018). Bayesian estimation of Gaussian -->
<!-- graphical models with predictive covariance selection. arXiv preprint -->
<!-- Working paper -->

<!-- Williams, D. R., & Martin, S. R. (2017). Rethinking robust statistics with modern Bayesian -->
<!-- methods. PsyArXiv. -->

<!-- Martin, S. R., & Williams, D. R. (2017). Outgrowing the Procrustean Bed of Normality: The -->
<!-- Utility of Bayesian Modeling for Asymmetrical Data Analysis. PsyArXiv. -->
<!-- Working paper -->
<!-- <!-- Working paper -->
<!-- --> 