---
title: "Publications"
favicon: images/headphones.JPG
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    css:
      - css/custom.css
---

<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons/css/academicons.min.css">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
library(distilltools)
```

```{r metathis, message=FALSE, warning=FALSE, include=FALSE}
library(metathis)
meta() %>%
  meta_description(
    "Open-Source Software"
  ) %>%
  meta_name("github-repo" = "donaldRwilliams/donaldRwilliams.github.io") %>%
  meta_viewport() %>%
  meta_social(
    title = "DRW: Software",
    url = "https://donaldrwilliams.github.io/publications.html",
    image = "https://donaldrwilliams.github.io/images/pub_preview.png",
    image_alt = "A photo of DRW",
    og_type = "website",
    og_author = c("Donald R. Williams"),
    twitter_card_type = "summary",
    twitter_creator = "@wdonald_1985"
  )
```

```{r, include=FALSE}
library(htmltools)
source("R/functions.R")
```







## Peer-Reviewed
### 2021
**Williams, D. R.** (in press). Learning to Live with Sampling Variability: 
Expected Replicability in Partial Correlation Networks. *Psychological Methods*.

```
@article{,
  title={Learning to live with sampling variability: Expected 
         replicability in partial correlation networks},
  author={Williams, Donald R},
  year={2020},
  journal={PsyArXiv},
  doi={10.31234/osf.io/fb4sa}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/fb4sa/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/uedkj/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)
```


<hr style="width:35%;text-align:left;margin-left:10">>  

**Williams, D. R.** (2021) Bayesian Estimation for Gaussian Graphical Models: 
Structure Learning, Predictability, and Network Comparisons, Multivariate Behavioral Research, 56:2, 336-352,  `r doi("10.1080/00273171.2021.1894412")` 

```
@article{,
  title={Bayesian estimation for Gaussian graphical models: 
         Structure learning, predictability, and network comparisons},
  author={Williams, Donald R},
  journal={Multivariate Behavioral Research},
  volume={56},
  number={2},
  pages={336--352},
  year={2021},
  publisher={Taylor \& Francis},
  doi = {10.1080/00273171.2021.1894412}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/x8dpr/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/k9mv2/"
  )

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)
```

<br>

**Williams, D. R.**, Martin, S. R., & Rast, P. (in press). Putting the Individual into Reliability: Bayesian Testing of Homogeneous Within-Person Variance in Hierarchical Models. *Behavior Research Methods*.


```
@article{,
  title={Putting the individual into reliability: 
         Bayesian testing of homogeneous within-person 
         variance in hierarchical models},
  author={Williams, Donald R and Martin, Stephen R and 
          Rast, Philippe},
  year={2019},
  publisher={PsyArXiv},
  doi={10.31234/osf.io/hpq7w}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/hpq7w/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/2qesh/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMncv/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/vICC"
)
```


<br>

**Williams, D. R.**, Liu, S., Martin, S. R., & Rast, P. (2021). Bayesian 
Multivariate Mixed-Effects Location Scale Modeling of Longitudinal Relations among 
Affective 
Traits, States, and Physical Activity.
European Journal of Psychological Assessment. 36 (6). `r doi("10.1027/1015-5759/a000624")`

```
@article{,
  title={Bayesian Multivariate Mixed-Effects Location 
         Scale Modeling of Longitudinal Relations among 
         Affective Traits, States, and Physical Activity},
  author={Williams, Donald R and Martin, Stephen R and Liu, 
          Siwei and Rast, Philippe},
  journal={European Journal of Psychological Assessment},
  year={2021},
  publisher={Hogrefe Publishing},
  doi={10.1027/1015-5759/a000624}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/4kfjp/"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/3bmdh/"
)
```

<br>

Mulder, J., **Williams, D. R.**, Gu, X., Olsson-Collentine, A., Tomarken, A., 
Boing-Messing, F., Hoijtink, H., ... & van Lissa, C. (in press). BFpack: Flexible bayes factor testing of scientific theories
in R. *Journal of Statistical Software*.

```
@article{mulder2019bfpack,
  title={BFpack: Flexible bayes factor testing 
         of scientific theories in r},
  author={Mulder, Joris and Gu, Xin and Olsson-Collentine, 
          Anton and Tomarken, Andrew and B{\"o}ing-Messing, 
          Florian and Hoijtink, Herbert and Meijerink, Marlyne 
          and Williams, Donald R and Menke, Janosch and Fox, 
          Jean-Paul and others},
  journal={arXiv preprint arXiv:1911.07728},
  year={2019}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://arxiv.org/pdf/1911.07728"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BFpack/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/jomulder/BFpack"
)

```





<br>

### 2020

**Williams, D. R.**, Mulder, J., Rouder, J. N., & Rast, P. (2020). 
Beneath the surface: Unearthing within-person variability and mean 
relations with Bayesian mixed models. *Psychological Methods*. 
`r doi("10.1037/met0000270")`

These analyses are reproduced at the GitHub repo.

```
@article{,
  title={Beneath the surface: Unearthing within-person variability 
         and mean relations with Bayesian mixed models.},
  author={Williams, Donald R and Mulder, Joris and Rouder, 
         Jeffrey N and Rast, Philippe},
  journal={Psychological Methods},
  year={2020},
  publisher={American Psychological Association},
  doi={10.1037/met0000270}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/gwatq/download"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/hypMuVar"
)
```


<br>

**Williams, D. R.** & Joris Mulder. Bayesian Hypothesis Testing for Gaussian Graphical Models: Conditional Independence and Order Constraints. *Journal of Mathematical Psychology*, 99, 102441. `r doi("10.1016/j.jmp.2020.102441")``

```
@article{,
  title={Bayesian hypothesis testing for Gaussian graphical models: 
         Conditional independence and order constraints},
  author={Williams, Donald R and Mulder, Joris},
  journal={Journal of Mathematical Psychology},
  volume={99},
  pages={102441},
  year={2020},
  publisher={Elsevier},
  doi = {10.1016/j.jmp.2020.102441}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/ypxd8/download"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)
```


<br>

**Williams, D. R.**, Rast, P., Pericchi, L. R., & Mulder, J. (2020). 
Comparing Gaussian graphical models with the posterior predictive 
distribution and Bayesian model selection. *Psychological methods*.
`r doi("10.1037/met0000254")``

```
@article{,
  title={Comparing Gaussian graphical models with the posterior 
  predictive distribution and Bayesian model selection.},
  author={Williams, DR and Rast, P and Pericchi, LR and Mulder, J},
  journal={Psychological Methods},
  volume={25},
  number={5},
  pages={653--672},
  year={2020},
  doi={10.1037/met0000254}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/yt386/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/7hyr4/"
  )

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)
```


<br>

**Williams, D. R.**, & Rast, P. (2020). Back to the basics: Rethinking 
partial correlation network methodology. *British Journal of Mathematical and Statistical Psychology*, 73(2), 187-212.  `r doi("10.1111/bmsp.12173")``


```
@article{,
  title={Back to the basics: Rethinking partial correlation network 
         methodology},
  author={Williams, Donald R and Rast, Philippe},
  journal={British Journal of Mathematical and Statistical Psychology},
  volume={73},
  number={2},
  pages={187--212},
  year={2020},
  publisher={Wiley Online Library},
  doi={10.1111/bmsp.12173}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/fndru/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/c62pb/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)
```


<br> 

**Williams, D. R.**, & Mulder, J. (2020). BGGM: Bayesian Gaussian Graphical 
Models in R. Journal of Open Source Software, 5(51), 2111. `r doi("10.21105/joss.02111")`

```
@article{,
  title={BGGM: Bayesian Gaussian Graphical Models in R},
  author={Williams, Donald R and Mulder, Joris},
  journal={Journal of Open Source Software},
  volume={5},
  number={51},
  pages={2111},
  year={2020},
  doi={10.21105/joss.02111}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://www.theoj.org/joss-papers/joss.02111/10.21105.joss.02111.pdf"
)


icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)
```

<br>

**Williams, D. R.**, & Burkner, P. (2020). Coding errors lead to unsupported conclusions: a critique of Hofmann et al. (2015). Meta-Psychology, 4.
`r doi("10.15626/MP.2018.872")`.

```
@article{,
  title={Coding errors lead to unsupported conclusions: 
         a critique of Hofmann et al.(2015)},
  author={Williams, Donald and B{\"u}rkner, Paul-Christian},
  journal={Meta-Psychology},
  volume={4},
  year={2020},
  doi={10.15626/MP.2018.872}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://open.lnu.se/index.php/metapsychology/article/view/872/2286"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/kd3en/"
)
```


<br>

Briganti, G., **Williams, D. R.**, Mulder, J., & Linkowski, P. (2020). Bayesian network structure and predictability of autistic traits.
*Psychological Reports*. `r doi("10.1177/0033294120978159")`.

```
@article{,
  title={Bayesian network structure and predictability
         of autistic traits},
  author={Briganti, Giovanni and Williams, Donald R
          and Mulder, Joris and Linkowski, Paul},
  journal={Psychological Reports},
  year={2020},
  doi={10.1177/0033294120978159}
}
```

<br>

Jones, P. J., Williams, D. R., & McNally, R. J. (2020).
Sampling variability is not nonreplication: A Bayesian reanalysis
of Forbes, Wright, Markon, and Krueger.
*Multivariate Behavioral Research*, 1-7.
`r doi("10.1080/00273171.2020.1797460")`


```
@article{,
  title={Sampling variability is not nonreplication: A Bayesian
         reanalysis of Forbes, Wright, Markon, and Krueger},
  author={Jones, Payton J and Williams, Donald R and McNally, Richard J},
  journal={Multivariate Behavioral Research},
  pages={1--7},
  year={2020},
  publisher={Taylor \& Francis},
  doi={10.1080/00273171.2020.1797460}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/egwfj/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/g5etn/"
)
```


<br>


Rast, P., Martin, S. R., Liu, S., & **Williams, D. R.** (2020). A new
frontier for studying within-person variability: Bayesian multivariate
generalized autoregressive conditional heteroskedasticity models.
*Psychological Methods*. `r doi("10.1037/met0000357")``


```
@article{,
  title={A new frontier for studying within-person
         variability: Bayesian multivariate generalized
         autoregressive conditional heteroskedasticity
         models.},
  author={Rast, P and Martin, SR and Liu, S and Williams, DR},
  journal={Psychological Methods},
  year={2020},
  doi = {10.1037/met0000357}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/j57pk/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/nef2q/"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/ph-rast/bmgarch"
)
```


<br>

### 2019

**Williams, D. R.**, Zimprich, D. R., & Rast, P. (2019). 
A Bayesian nonlinear mixed-effects location
scale model for learning. *Behavior research methods*, 51(5), 
1968-1986. `r doi("10.3758/s13428-019-01255-9")`.


```
@article{,
  title={A Bayesian nonlinear mixed-effects location 
         scale model for learning},
  author={Williams, Donald R and Zimprich, Daniel R 
          and Rast, Philippe},
  journal={Behavior research methods},
  volume={51},
  number={5},
  pages={1968--1986},
  year={2019}, 
  doi{10.3758/s13428-019-01255-9}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://link.springer.com/content/pdf/10.3758/s13428-019-01255-9.pdf"
)
```


<br>

**Williams, D. R.**, Rhemtulla, M., Wysocki, A. C., & Rast, P. (2019). On nonregularized estimation of psychological networks. *Multivariate behavioral research*, 54(5), 719-750. `r doi("10.1080/00273171.2019.1575716")`.

```
@article{,
  title={On nonregularized estimation of psychological 
         networks},
  author={Williams, Donald R and Rhemtulla, Mijke and 
          Wysocki, Anna C and Rast, Philippe},
  journal={Multivariate behavioral research},
  volume={54},
  number={5},
  pages={719--750},
  year={2019},
  doi={10.1080/00273171.2019.1575716}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/xr2vf/download"
)

icon_link(
    icon = "fab fa-github",
    text = "Repo",
    url  = "https://github.com/donaldRwilliams/on_nonregularized_networks"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)
```


<br>

Nalborczyk, L., Burkner, P. C., & **Williams, D. R.** (2019). Pragmatism 
should not be a substitute for statistical literacy, a commentary on Albers, 
Kiers, and van Ravenzwaaij (2019). *Collabra: Psychology*,
5(1). `r doi("10.1525/collabra.197")`


```
@article{,
  title={Pragmatism should not be a substitute for statistical 
         literacy, a commentary on Albers, Kiers, and 
         van Ravenzwaaij (2018)},
  author={Nalborczyk, Ladislas and B{\"u}rkner, Paul-Christian 
          and Williams, Donald R and Savalei, Victoria},
  journal={Collabra: Psychology},
  volume={5},
  number={1},
  year={2019},
  doi={10.1525/collabra.197}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://online.ucpress.edu/collabra/article-pdf/5/1/13/437386/197-2975-1-pb.pdf"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/nmp6x/"
)
```




<br>

### 2018

Quintana, D. S., & **Williams, D. R.** (2018). Bayesian alternatives for 
common null-hypothesis significance tests in psychiatry: a non-technical 
guide using JASP. BMC psychiatry, 18(1), 178. 
`r doi("10.1186/s12888-018-1761-4")`

```
@article{,
  title={Bayesian alternatives for common null-hypothesis significance 
         tests in psychiatry: a non-technical guide using JASP},
  author={Quintana, Daniel S and Williams, Donald R},
  journal={BMC psychiatry},
  volume={18},
  number={1},
  pages={1--8},
  year={2018},
  doi={10.1186/s12888-018-1761-4}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://bmcpsychiatry.biomedcentral.com/track/pdf/10.1186/s12888-018-1761-4.pdf"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/emz4r/"
)
```
