---
title: "Publications"
favicon: images/headphones.JPG
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    css:
      - css/custom.css
---

<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons/css/academicons.min.css">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(file.path("R", "functions.R"))
library(distilltools)
```

```{r metathis, message=FALSE, warning=FALSE, include=FALSE}
library(metathis)
meta() %>%
  meta_description(
    "Open-Source Software"
  ) %>%
  meta_name("github-repo" = "donaldRwilliams/donaldRwilliams.github.io") %>%
  meta_viewport() %>%
  meta_social(
    title = "DRW: Software",
    url = "https://donaldrwilliams.github.io/publications.html",
    image = "https://donaldrwilliams.github.io/images/pub_preview.png",
    image_alt = "A photo of DRW",
    og_type = "website",
    og_author = c("Donald R. Williams"),
    twitter_card_type = "summary",
    twitter_creator = "@wdonald_1985"
  )
```

```{r, include=FALSE}
library(htmltools)
source("R/functions.R")
```







## Peer-Reviewed

First author: 16 

* Highlights  (all first author)
  + Psychological Methods: 3 (including 1 solo author)
  + Multivariate Behavioral Research: 2 (including 1 solo author)
  + Behavior Research Methods: 2
  + Journal of Mathematical Psychology: 1

<font size="2"> (note: 9 first author manuscripts are in review. 
see pre-prints.)</font> 


### 2021
**Williams, D. R.** (in press). Learning to Live with Sampling Variability: 
Expected Replicability in Partial Correlation Networks. *Psychological Methods*.

```
@article{,
  title={Learning to live with sampling variability: Expected 
         replicability in partial correlation networks},
  author={Williams, Donald R},
  year={2020},
  journal={PsyArXiv},
  doi={10.31234/osf.io/fb4sa}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/fb4sa/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/uedkj/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.** (2021) Bayesian Estimation for Gaussian Graphical Models: 
Structure Learning, Predictability, and Network Comparisons, Multivariate Behavioral Research, 56:2, 336-352,  `r doi("10.1080/00273171.2021.1894412")` 

```
@article{,
  title={Bayesian estimation for Gaussian graphical models: 
         Structure learning, predictability, and network comparisons},
  author={Williams, Donald R},
  journal={Multivariate Behavioral Research},
  volume={56},
  number={2},
  pages={336--352},
  year={2021},
  publisher={Taylor \& Francis},
  doi = {10.1080/00273171.2021.1894412}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/x8dpr/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/k9mv2/"
  )

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, Martin, S. R., & Rast, P. (in press). Putting the Individual into Reliability: Bayesian Testing of Homogeneous Within-Person Variance in Hierarchical Models. *Behavior Research Methods*.


```
@article{,
  title={Putting the individual into reliability: 
         Bayesian testing of homogeneous within-person 
         variance in hierarchical models},
  author={Williams, Donald R and Martin, Stephen R and 
          Rast, Philippe},
  year={2019},
  publisher={PsyArXiv},
  doi={10.31234/osf.io/hpq7w}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/hpq7w/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/2qesh/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMncv/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/vICC"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, Liu, S., Martin, S. R., & Rast, P. (2021). Bayesian 
Multivariate Mixed-Effects Location Scale Modeling of Longitudinal Relations among 
Affective 
Traits, States, and Physical Activity.
European Journal of Psychological Assessment. 36 (6). `r doi("10.1027/1015-5759/a000624")`

```
@article{,
  title={Bayesian Multivariate Mixed-Effects Location 
         Scale Modeling of Longitudinal Relations among 
         Affective Traits, States, and Physical Activity},
  author={Williams, Donald R and Martin, Stephen R and Liu, 
          Siwei and Rast, Philippe},
  journal={European Journal of Psychological Assessment},
  year={2021},
  publisher={Hogrefe Publishing},
  doi={10.1027/1015-5759/a000624}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/4kfjp/"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/3bmdh/"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

Mulder, J., **Williams, D. R.**, Gu, X., Olsson-Collentine, A., Tomarken, A., 
Boing-Messing, F., Hoijtink, H., ... & van Lissa, C. (in press). BFpack: Flexible bayes factor testing of scientific theories
in R. *Journal of Statistical Software*.

```
@article{mulder2019bfpack,
  title={BFpack: Flexible bayes factor testing 
         of scientific theories in r},
  author={Mulder, Joris and Gu, Xin and Olsson-Collentine, 
          Anton and Tomarken, Andrew and B{\"o}ing-Messing, 
          Florian and Hoijtink, Herbert and Meijerink, Marlyne 
          and Williams, Donald R and Menke, Janosch and Fox, 
          Jean-Paul and others},
  journal={arXiv preprint arXiv:1911.07728},
  year={2019}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://arxiv.org/pdf/1911.07728"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BFpack/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/jomulder/BFpack"
)

```

<hr style="width:35%;text-align:left;margin-left:15">  

### 2020

**Williams, D. R.**, Mulder, J., Rouder, J. N., & Rast, P. (2020). 
Beneath the surface: Unearthing within-person variability and mean 
relations with Bayesian mixed models. *Psychological Methods*. 
`r doi("10.1037/met0000270")`

These analyses are reproduced at the GitHub repo.

```
@article{,
  title={Beneath the surface: Unearthing within-person variability 
         and mean relations with Bayesian mixed models.},
  author={Williams, Donald R and Mulder, Joris and Rouder, 
         Jeffrey N and Rast, Philippe},
  journal={Psychological Methods},
  year={2020},
  publisher={American Psychological Association},
  doi={10.1037/met0000270}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/gwatq/download"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/hypMuVar"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.** & Joris Mulder. Bayesian Hypothesis Testing for Gaussian Graphical Models: Conditional Independence and Order Constraints. *Journal of Mathematical Psychology*, 99, 102441. `r doi("10.1016/j.jmp.2020.102441")``

```
@article{,
  title={Bayesian hypothesis testing for Gaussian graphical models: 
         Conditional independence and order constraints},
  author={Williams, Donald R and Mulder, Joris},
  journal={Journal of Mathematical Psychology},
  volume={99},
  pages={102441},
  year={2020},
  publisher={Elsevier},
  doi = {10.1016/j.jmp.2020.102441}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/ypxd8/download"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, Rast, P., Pericchi, L. R., & Mulder, J. (2020). 
Comparing Gaussian graphical models with the posterior predictive 
distribution and Bayesian model selection. *Psychological methods*.
`r doi("10.1037/met0000254")``

```
@article{,
  title={Comparing Gaussian graphical models with the posterior 
  predictive distribution and Bayesian model selection.},
  author={Williams, DR and Rast, P and Pericchi, LR and Mulder, J},
  journal={Psychological Methods},
  volume={25},
  number={5},
  pages={653--672},
  year={2020},
  doi={10.1037/met0000254}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/yt386/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/7hyr4/"
  )

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, & Rast, P. (2020). Back to the basics: Rethinking 
partial correlation network methodology. *British Journal of Mathematical and Statistical Psychology*, 73(2), 187-212.  `r doi("10.1111/bmsp.12173")``


```
@article{,
  title={Back to the basics: Rethinking partial correlation network 
         methodology},
  author={Williams, Donald R and Rast, Philippe},
  journal={British Journal of Mathematical and Statistical Psychology},
  volume={73},
  number={2},
  pages={187--212},
  year={2020},
  publisher={Wiley Online Library},
  doi={10.1111/bmsp.12173}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/fndru/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/c62pb/"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, & Mulder, J. (2020). BGGM: Bayesian Gaussian Graphical 
Models in R. Journal of Open Source Software, 5(51), 2111. `r doi("10.21105/joss.02111")`

```
@article{,
  title={BGGM: Bayesian Gaussian Graphical Models in R},
  author={Williams, Donald R and Mulder, Joris},
  journal={Journal of Open Source Software},
  volume={5},
  number={51},
  pages={2111},
  year={2020},
  doi={10.21105/joss.02111}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://www.theoj.org/joss-papers/joss.02111/10.21105.joss.02111.pdf"
)


icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/BGGM/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/BGGM"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "Website",
    url  = "https://donaldrwilliams.github.io/BGGM/"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, & Burkner, P. (2020). Coding errors lead to unsupported conclusions: a critique of Hofmann et al. (2015). Meta-Psychology, 4.
`r doi("10.15626/MP.2018.872")`.

```
@article{,
  title={Coding errors lead to unsupported conclusions: 
         a critique of Hofmann et al.(2015)},
  author={Williams, Donald and B{\"u}rkner, Paul-Christian},
  journal={Meta-Psychology},
  volume={4},
  year={2020},
  doi={10.15626/MP.2018.872}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://open.lnu.se/index.php/metapsychology/article/view/872/2286"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/kd3en/"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

Briganti, G., **Williams, D. R.**, Mulder, J., & Linkowski, P. (2020). Bayesian network structure and predictability of autistic traits.
*Psychological Reports*. `r doi("10.1177/0033294120978159")`.

```
@article{,
  title={Bayesian network structure and predictability
         of autistic traits},
  author={Briganti, Giovanni and Williams, Donald R
          and Mulder, Joris and Linkowski, Paul},
  journal={Psychological Reports},
  year={2020},
  doi={10.1177/0033294120978159}
}
```

<hr style="width:35%;text-align:left;margin-left:15">  

Jones, P. J., **Williams, D. R.**, & McNally, R. J. (2020).
Sampling variability is not nonreplication: A Bayesian reanalysis
of Forbes, Wright, Markon, and Krueger.
*Multivariate Behavioral Research*, 1-7.
`r doi("10.1080/00273171.2020.1797460")`


```
@article{,
  title={Sampling variability is not nonreplication: A Bayesian
         reanalysis of Forbes, Wright, Markon, and Krueger},
  author={Jones, Payton J and Williams, Donald R and McNally, Richard J},
  journal={Multivariate Behavioral Research},
  pages={1--7},
  year={2020},
  publisher={Taylor \& Francis},
  doi={10.1080/00273171.2020.1797460}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/egwfj/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/g5etn/"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

Rast, P., Martin, S. R., Liu, S., & **Williams, D. R.** (2020). A new
frontier for studying within-person variability: Bayesian multivariate
generalized autoregressive conditional heteroskedasticity models.
*Psychological Methods*. `r doi("10.1037/met0000357")``


```
@article{,
  title={A new frontier for studying within-person
         variability: Bayesian multivariate generalized
         autoregressive conditional heteroskedasticity
         models.},
  author={Rast, P and Martin, SR and Liu, S and Williams, DR},
  journal={Psychological Methods},
  year={2020},
  doi = {10.1037/met0000357}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/j57pk/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/nef2q/"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/ph-rast/bmgarch"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

### 2019

**Williams, D. R.**, Zimprich, D. R., & Rast, P. (2019). 
A Bayesian nonlinear mixed-effects location
scale model for learning. *Behavior research methods*, 51(5), 
1968-1986. `r doi("10.3758/s13428-019-01255-9")`.


```
@article{,
  title={A Bayesian nonlinear mixed-effects location 
         scale model for learning},
  author={Williams, Donald R and Zimprich, Daniel R 
          and Rast, Philippe},
  journal={Behavior research methods},
  volume={51},
  number={5},
  pages={1968--1986},
  year={2019}, 
  doi{10.3758/s13428-019-01255-9}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://link.springer.com/content/pdf/10.3758/s13428-019-01255-9.pdf"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, Rhemtulla, M., Wysocki, A. C., & Rast, P. (2019). On nonregularized estimation of psychological networks. *Multivariate behavioral research*, 54(5), 719-750. `r doi("10.1080/00273171.2019.1575716")`.

```
@article{,
  title={On nonregularized estimation of psychological 
         networks},
  author={Williams, Donald R and Rhemtulla, Mijke and 
          Wysocki, Anna C and Rast, Philippe},
  journal={Multivariate behavioral research},
  volume={54},
  number={5},
  pages={719--750},
  year={2019},
  doi={10.1080/00273171.2019.1575716}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/xr2vf/download"
)

icon_link(
    icon = "fab fa-github",
    text = "Repo",
    url  = "https://github.com/donaldRwilliams/on_nonregularized_networks"
)

icon_link(
    icon = "fas fa-external-link-alt",
    text = "CRAN",
    url  = "https://cran.r-project.org/web/packages/GGMnonreg/index.html"
)

icon_link(
    icon = "fab fa-github",
    text = "GitHub",
    url  = "https://github.com/donaldRwilliams/GGMnonreg"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

Nalborczyk, L., Burkner, P. C., & **Williams, D. R.** (2019). Pragmatism 
should not be a substitute for statistical literacy, a commentary on Albers, 
Kiers, and van Ravenzwaaij (2019). *Collabra: Psychology*,
5(1). `r doi("10.1525/collabra.197")`


```
@article{,
  title={Pragmatism should not be a substitute for statistical 
         literacy, a commentary on Albers, Kiers, and 
         van Ravenzwaaij (2018)},
  author={Nalborczyk, Ladislas and B{\"u}rkner, Paul-Christian 
          and Williams, Donald R and Savalei, Victoria},
  journal={Collabra: Psychology},
  volume={5},
  number={1},
  year={2019},
  doi={10.1525/collabra.197}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://online.ucpress.edu/collabra/article-pdf/5/1/13/437386/197-2975-1-pb.pdf"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/nmp6x/"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

### 2018

Quintana, D. S., & **Williams, D. R.** (2018). Bayesian alternatives for 
common null-hypothesis significance tests in psychiatry: a non-technical 
guide using JASP. BMC psychiatry, 18(1), 178. 
`r doi("10.1186/s12888-018-1761-4")`

```
@article{,
  title={Bayesian alternatives for common null-hypothesis significance 
         tests in psychiatry: a non-technical guide using JASP},
  author={Quintana, Daniel S and Williams, Donald R},
  journal={BMC psychiatry},
  volume={18},
  number={1},
  pages={1--8},
  year={2018},
  doi={10.1186/s12888-018-1761-4}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://bmcpsychiatry.biomedcentral.com/track/pdf/10.1186/s12888-018-1761-4.pdf"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/emz4r/"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

Lakens, D., Adol, F. G., Albers, C. J., Anvari, F., Apps, M. A., Argamon, S. E., ... & Buchanan, E. M. (2018). Justify your alpha. *Nature Human Behaviour*, 2(3), 168.


```
@article{,
  title={Justify your alpha},
  author={Lakens, Daniel and Adolfi, Federico G and Albers, 
          Casper J and Anvari, Farid and Apps, Matthew AJ 
          and Argamon, Shlomo E and Baguley, Thom and Becker, 
          Raymond B and Benning, Stephen D and Bradford, 
          Daniel E and others},
  journal={Nature Human Behaviour},
  volume={2},
  number={3},
  pages={168--171},
  year={2018},
  doi={10.1038/s41562-018-0311-x}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/9s3y6/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/by2kc/"
)
```


<hr style="width:35%;text-align:left;margin-left:15"> 

Carlsson, R., Agerstrom, J., **Williams, D.R**, & Burns, G. N. (2018). A Primer on the benenits of differential treatment analysis when predicting discriminatory behavior. *Quantitative Methods for Psychology*, 14(3), 193-198. 
`r doi("10.20982/tqmp.14.3.p193")`.

```
@article{,
  title={A Primer on the benefits of differential treatment analysis 
         when predicting discriminatory behavior},
  author={Carlsson, Rickard and Agerstr{\"o}m, Jens and Williams, 
          Donald and Burns, Gary N},
  journal={Quantitative Methods for Psychology},
  volume={14},
  number={3},
  pages={193--198},
  year={2018},
  doi={10.20982/tqmp.14.3.p193}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "http://www.tqmp.org/RegularArticles/vol14-3/p193/p193.pdf"
)
```


<hr style="width:35%;text-align:left;margin-left:15"> 


Merritt, J. R., Davis, M. T., Jalabert, C., Libecap, T. J., **Williams, D. R.**, Soma, K. K., & Maney, D. L. (2018). Rapid effects of estradiol on aggression 
depend on genotype in a species with an estrogen receptor polymorphism. 
Hormones and behavior, 98, 210-218. `r doi("10.1016/j.yhbeh.2017.11.014")``

```
@article{merritt2018rapid,
  title={Rapid effects of estradiol on aggression depend 
         on genotype in a species with an estrogen receptor 
         polymorphism},
  author={Merritt, Jennifer R and Davis, Matthew T and 
          Jalabert, Cecilia and Libecap, Timothy J and Williams, 
          Donald R and Soma, Kiran K and Maney, Donna L},
  journal={Hormones and behavior},
  volume={98},
  pages={210--218},
  year={2018},
  doi={10.1016/j.yhbeh.2017.11.014}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fas fa-external-link-alt",
    text = "Journal",
    url  = "https://www.sciencedirect.com/science/article/abs/pii/S0018506X17303501"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

### 2017

**Williams, D. R.**, Carlsson, R., & Burkner, P. C. (2017). Between-litter 
variation in developmental studies of hormones and behavior: In
ated false positives and diminished power. Frontiers in
neuroendocrinology, 47, 154-166. `r doi("10.1016/j.yfrne.2017.08.003")`


```
@article{,
  title={Between-litter variation in developmental studies 
         of hormones and behavior: inflated false positives 
         and diminished power},
  author={Williams, Donald R and Carlsson, Rickard 
         and B{\"u}rkner, Paul-Christian},
  journal={Frontiers in neuroendocrinology},
  volume={47},
  pages={154--166},
  year={2017},
  doi={10.1016/j.yfrne.2017.08.003}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/97xjz/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/fxy7h/"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, & Burkner, P. C. (2017). Effects of intranasal oxytocin 
on symptoms of schizophrenia: a multivariate Bayesian meta-analysis. *Psychoneuroendocrinology*, 75, 141-151. 
`r doi("10.1016/j.psyneuen.2016.10.013")`


```
@article{,
  title={Effects of intranasal oxytocin on symptoms of 
         schizophrenia: A multivariate Bayesian 
         meta-analysis},
  author={Williams, Donald R and B{\"u}rkner, Paul-Christian},
  journal={Psychoneuroendocrinology},
  volume={75},
  pages={141--151},
  year={2017},
  doi={10.1016/j.psyneuen.2016.10.013}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/qf5zn/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/6pyfu/"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

Burkner, P. C., **Williams, D. R.**$^*$, Simmons, T. C., & Woolley, J. D. 
(2017). Intranasal oxytocin may improve high-level social cognition 
in Schizophrenia, but not social cognition or neurocognition in
general: a multilevel bayesian meta-analysis. *Schizophrenia Bulletin*, 
43(6), 1291-1303. `r doi("10.1093/schbul/sbx053")``

$^*$ shared 1st authorship


```
@article{,
  title={Intranasal oxytocin may improve high-level social 
         cognition in schizophrenia, but not social cognition 
         or neurocognition in general: a multilevel bayesian 
         meta-analysis},
  author={B{\"u}rkner, Paul-Christian and Williams, 
         Donald R and Simmons, Trenton C and Woolley, Josh D},
  journal={Schizophrenia Bulletin},
  volume={43},
  number={6},
  pages={1291--1303},
  year={2017},
  doi={10.1093/schbul/sbx053}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/2a4yt/"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/rn6vj/"
)
```


<hr style="width:35%;text-align:left;margin-left:15">  

**Williams, D. R.**, & Burkner, P. C. (2017). Data extraction and 
statistical errors: A quantitative critique of Gumley, 
Braehler, and Macbeth (2014). *British Journal of Clinical 
Psychology*, 56(2), 208-211. `r doi("10.1111/bjc.12130")`

```
@article{,
  title={Data extraction and statistical errors: 
         A quantitative critique of Gumley, 
         Braehler, and Macbeth (2014)},
  author={Williams, Donald R and B{\"u}rkner, Paul-Christian},
  journal={British Journal of Clinical Psychology},
  volume={56},
  number={2},
  pages={208--211},
  year={2017},
  doi = {10.1111/bjc.12130}
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/bw2ce/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/bw2ce/"
)
```

<hr style="width:35%;text-align:left;margin-left:15">  

Carlsson, R., Schimmack, U., **Williams, D. R.**, & Burkner, P. C. (2017).
Bayes factors from pooled data are no substitute for 
Bayesian meta-Analysis: commentary on Scheibehenne, Jamil, 
and Wagenmakers (2016). *Psychological science*, 28(11), 1694-1697.
`r doi("10.1177/0956797616684682")``

```
@article{,
  title={Bayes factors from pooled data are no substitute 
         for Bayesian meta-analysis: Commentary on Scheibehenne, 
         Jamil, and Wagenmakers (2016)},
  author={Carlsson, Rickard and Schimmack, 
          Ulrich and Williams, Donald R and B{\"u}rkner, 
          Paul-Christian},
  journal={Psychological Science},
  volume={28},
  number={11},
  pages={1694--1697},
  year={2017},
  doi={"10.1177/0956797616684682"}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://osf.io/axhsr/download"
)

icon_link(
    icon = "ai ai-osf",
    text = "Repo",
    url  = "https://osf.io/6g9su/components?mode=&view_only="
)
```


<hr style="width:35%;text-align:left;margin-left:15">  


Maninger, N., Mendoza, S. P., **Williams, D. R.**, Mason, W. A., 
Cherry, S. R., 
Rowland, D. J., ... & Bales, K. L. (2017). Imaging, behavior and 
endocrine analysis of "Jealousy" in a monogamous primate.
*Frontiers in ecology and evolution*, 5, 119.
`r doi("10.3389/fevo.2017.00119")`

```
@article{,
  title={Imaging, behavior and endocrine analysis of 
        “jealousy” in a monogamous primate},
  author={Maninger, Nicole and Mendoza, Sally P and Williams, 
          Donald R and Mason, William A and Cherry, Simon R 
          and Rowland, Douglas J and Schaefer, Thomas and Bales, Karen L},
  journal={Frontiers in ecology and evolution},
  volume={5},
  pages={119},
  year={2017},
  doi={10.3389/fevo.2017.00119}
}
```

```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://www.frontiersin.org/articles/10.3389/fevo.2017.00119/pdf"
)
```



<hr style="width:35%;text-align:left;margin-left:15">  

Bales, K. L., del Razo, R. A., Conklin, Q. A., Hartman, S., 
Mayer, H. S., Rogers, F. D., ... & Witczak, L. R. (2017). 
Focus: Comparative medicine: Titi monkeys as a novel non-human 
primate model for the neurobiology of pair bonding. 
The Yale journal of biology and medicine, 90(3), 373.



```
@article{,
  title={Focus: comparative medicine: Titi monkeys as a 
         novel non-human primate model for the neurobiology 
         of pair bonding},
  author={Bales, Karen L and Del Razo, Roc{\'\i}o Arias and 
          Conklin, Quinn A and Hartman, Sarah and Mayer, 
          Heather S and Rogers, Forrest D and Simmons, Trenton 
          C and Smith, Leigh K and Williams, Alexia and Williams, 
          Donald R and others},
  journal={The Yale journal of biology and medicine},
  volume={90},
  number={3},
  pages={373},
  year={2017},
}
```


```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5612182/pdf/yjbm_90_3_373.pdf"
)
```




<br>
<br>

## Pre-Prints


First author: 9

* Highlights  (all first author)
  + Psychological Methods: 3
  + Multivariate Behavioral Research: 2
  + Behavior Research Methods: 1
  + Psychometrika: 1
  + Journal of Open-Source Software: 1
  + R Journal: 1

<font size="2"> (note: status provided below.)</font> 

<hr style="width:35%;text-align:left;margin-left:15">

### 2021

**Williams, D. R.**, Rodriguez, J. E., & Burkner, P. (2021). 
Putting Variation into Variance: Modeling Between-Study 
Heterogeneity in Meta-Analysis. *PsyArXiv*. 
`r doi("10.31234/osf.io/9vkqy")`

*Psychological Methods*: submitted

The code to reproduce the analyses is on GitHub.


```
@article{,
  title={Putting Variation into Variance: Modeling Between-Study 
         Heterogeneity in Meta-Analysis},
  author={Williams, Donald R and Rodriguez, Josue E and 
          B{\"u}rkner, Paul-Christian},
  year={2021},
  journal={PsyArXiv},
  doi = {10.31234/osf.io/9vkqy}
}
```
```{r, echo=FALSE}
icon_link(
    icon = "fa fa-file-pdf",
    text = "PDF",
    url  = "https://psyarxiv.com/9vkqy/download"
)

icon_link(
    icon = "fab fa-github",
    text = "Repo",
    url  = "https://github.com/donaldRwilliams/putting_variance_blsmeta"
)

icon_link(
    icon = "fab fa-github",
    text = "Package",
    url  = "https://github.com/donaldRwilliams/blsmeta"
)
```
